%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Chao Wen Chen}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{
    % \\LinkedIn : https://www.linkedin.com/in/chao-wen-chen-5a0a61169/
\\ \\Github : https://github.com/George0112\\}
\address{\\chaowen.nthu@gmail.com \\(+886) 931875878}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}
%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
{\sl First year student in ISA@NTHU. Inquisitive, hard-working and consistent. Looking for internship opportunities apply my skills and contribute to real-world projects. }

\section{EDUCATION}
\textbf{National Tsing Hua University}, Taiwan\\
{\sl Bachelor of Engineering}, Computer Science and Engineering(CSE)\\
\textbf{National Tsing Hua University}, Taiwan \\
{\sl Master of Engineering}, Institute of Information Systems and Applications(ISA) 
%\hfill CGPA: 7.34/10.00\\
%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{TECHNICAL\\SKILLS}

\textbf{Experienced : } AWS, Kubernetes, SQL, Docker
\\
\textbf{Tools/Framework : } Laravel, Vue.js, SwiftUI, React.js, Express, Django
\\
\textbf{Languages : } Javascript, Python, PHP, C/C++, HTML/CSS

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\textbf{Cloud Security Intern at IBM \hfill{Jul 20 -}\\}
\normalfont{We use IBM Cloud Security technology and leverage threat intelligence and SOAR to solve the threat management problem of Taiwan financial industries}

\textbf{Network Manager of CSCC@NTHU \hfill{Aug 19 - }\\}
\normalfont{I'm responsible for all the network utilities belong to the department of Computer Science. The job encludes IP management, abuse of network reporting, new function development, etc.}

\textbf{Summer Intern of Administration Yuan \hfill{Jul 18 - Aug 18}\\}
\normalfont{It's a project for checking and revising websites of all departments of the gonvernment. I checked hundreds of websites and give them advices to make it better for daily and mobile usages.}

\textbf{Research Assistant of NMSL@NTHU \hfill{Jun 17 - }\\}
\normalfont{Our research field covers network and all kinds of media. With the trend of AI, we are looking for a better machine learning platfrom to accelerate the development of all kinds of models and improve them even after deployed.}

\textbf{Website Administrator and Developer of ITRI \hfill{Jun 17 - Mar 19}\\}
\normalfont{We developed a website for paper searching and recommending. More than a thousand people have registered and more than 2000 papers are included in this website.}

\section{PROJECTS}

\textbf{City in my Drone}\\
A cloud based project for controlling and streaming videos of drones. We orchestrates multiple AWS services such as EC2, S3, lambda, SQS, etc. With this project, we can remote control the drone with user-defined destinations or routes. I also built an IOS app using SwiftUI from scratch.
\\
\begin{itemize}
    \item \textbf{App: } https://github.com/George0112/DroneMaster
    \item \textbf{Demo:} https://www.youtube.com/watch?v=FEIgZtJsIbk
\end{itemize}

\textbf{Website of Butterfly Garden}\\
We reconstruct a brand new website of Butterfly Garden in NTHU since the old one isn't suitable for mobile devices. We redesign the database, and follows the MVC pattern by using Laravel and Vue.
\\
\begin{itemize}
    \item \textbf{Link:} http://belc-butterfly.vm.nthu.edu.tw
\end{itemize}

\textbf{Streaming Scalable Video Sequences with Media-Aware Network Elements}\\
Realizing a media-aware network element based on P4, an SDN language. We conduct experiments with bmv2 and SVEF. The result shows that we can maintain stable video streaming than regular switches.
\\
\begin{itemize}
    \item \textbf{Link:} https://ieeexplore.ieee.org/abstract/document/8406129
\end{itemize}

\textbf{Smart Manufacturing Digital Library \hfill{}}\\
A Laravel based website includes thousands of papers with well arrangement and recommendation. This website can recommend you papers chosen by experts in ITRI and we carefully designed RESTful APIs and follow MVC pattern.
\\
\begin{itemize}
    \item \textbf{Link:} https://industry4.tw/
\end{itemize}

\section{Publications}
\par
\normalfont{}

\normalfont{[1] G. Wang, \textbf{C. Chen}, C. Chen, L. Pan, Y. Wang, C. Fan, and C. Hsu, "Streaming scalable video sequences with media-aware network elements implemented in P4
programming language," in Proc. of IEEE Network Operations and Management Symposium (NOMS’18) Demo Session, Taipei, Taiwan, April 2018, pp. 1–2.}

\normalfont{[2] Q. Zhu, M. Uddin, N. Venkatasubramanian, \textbf{C. Chen}, and C. Hsu, "Spatio-temporal scheduling of in-Situ and mobile Internet-of-Things devices for urban
environment sensing," Ongoing Work.}

\normalfont{[3] \textbf{C. Chen}, T. Hong, and C. Hsu, "Essential Components of Modern Machine Learning
Platforms," Ongoing Work.}

\section{Research Grant}{}
\normalfont{[1] Streaming scalable video Sequences with media-aware network elements, MOST Undergraduate Research Project (\#107-2813-C-007 -074 -E), \$48,000, July 2018 - February 2019}

% \\
% \section{Course Design}{}
% \\
% \normalfont{[1] Software Defined Network Practice in P4 and ONOS}

\end{resume}
\(\)\end{document}